---
title: "ejscreen-group-14"
author: "Annie Combs" "Logan Ossentjuk"
date: "November 17, 2021"
output: html_document
---

### Set up 
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(janitor)
library(here)
```


### Read In Data 
```{r}
ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names() #convert column names to lower_snake_case
```

### Data Visualization
```{r}
ggplot(data = ces) +
  geom_hex(aes( x = white_percent, y = ces_3_0_score)) +
  scale_fill_gradient(low = "blue", high = "yellow") +
  theme_minimal() +
  labs(x = "Percent White Population", y = "CalEnviroScreen Pollution Score", title = "2010 US White Population Percentage vs CalEnviroScreen 3.0 Pollution Score")
```

**Figure 1: Percentage White vs CES Score.** Described above is the relationship between a college's percentage of white students and its CES score. Count is indicated by the color gradient of the hex plot. Schools with the highest percentage of white students had the lowest CES scores on average. 

It is evident here that as the percent of the population that is white increases, the CalEnviroScreen Pollution score decreases. This demonstrates how communities of color often bear a higher prevalence of pollution paired with health characteristics that increase pollutant-caused fatalities. 

*Data Citation*: Office of Environmental Health and Hazard Assessment (2018). CalEnviroScreen 3.0 Results. http://oehha.ca.gov/calenviroscreen/report/calenviroscreen-30

